---
title: "Assignment 7"
author: Artie Maharaj
output: html_notebook
---

1. Create a function that accepts (1) a quantitative response variable, (2) a quantitative explantory variable, and (3)a number. Suppose we denote the repsonse variable as y, the explantory variable as x, and the number as p. Your function should model y as a linear function of x and ten for each(x,y) pair determine if the residual is one of the p largest in the set of residuals, with largest defined in terms iof absolute value (e.g., a residual of -10 is just as large as a residual of 10). The function should return a logical vector indicating TRUE for each pair that has one of the pth largest residuals and FALSE otherwise. 
```{r}
Linear.model.top.residuals <- function (x, y, p...) {
  
linear.model <- lm(y~x)
model.residuals <-abs(linear.model$residuals)
sort.residuals <-sort(model.residuals$residuals, decreasing = TRUE)
top.ten.percent <- head(sort.residuals$residuals, p)
largest.res <- sort.residuals[p]
logical <-(model.residuals>=largest.res) 
return(logical)

}
```

2. Obtain a real dataset with quantitative response and explantory variable (n>=50). Plot these on a scatterplot with a regression line. Use your function to help you highlight the 10% largest residuals on the scatterplot.

Here I am using the dataset iris which describe the lengths and widths of petals of various species of iris plants. I am looking at whether petal width predicts petal length.
n = 150
x = petal width
y= petal length
p=15

```{r}
data(iris)
iris <- data.frame(iris)
```
Linear model
```{r}
Top.residuals<-Linear.model.top.residuals(iris$Petal.Length~iris$Petal.Width, 15)
summary(iris.model)
```

Here I will plot petal length with petal width.

```{r}
plot(iris$Petal.Length, iris$Petal.Width, main="Scatterplot of Iris petal length by width",
   xlab="Petal width ", ylab="Petal length", 
   col =ifelse(Top.residuals ))

```

