---
title: "Assignment 7"
author: Artie Maharaj
output: html_notebook
---

1. Create a function that accepts (1) a quantitative response variable, (2) a quantitative explantory variable, and (3)a number. Suppose we denote the repsonse variable as y, the explantory variable as x, and the number as p. Your function should model y as a linear function of x and ten for each(x,y) pair determine if the residual is one of the p largest in the set of residuals, with largest defined in terms iof absolute value (e.g., a residual of -10 is just as large as a residual of 10). The function should return a logical vector indicating TRUE for each pair that has one of the pth largest residuals and FALSE otherwise. 
```{r}
iris.model <- function (x, y, p...) {

  response.variable <- c(1:length(response.variable))
  
  explanatory.variable <- c(1:length(explantory.variable))
  return(explanatory.variable)
  
  p=15
  
  t_test <- function(x,y) {
  result <- t.test(x, y, paired = TRUE, conf.level = 0.95)
  return (result)
}
  
  
}
```
2. Obtain a real dataset with quantitative response and explantory variable (n>=50). Plot these on a scatterplot wiht a regression line. Use your function to help you highlight the 1% largest residuals on the scatterplot.

Here I am using the dataset iris. 
```{r}
data(iris)
```
Here I will plot petal length with petal width.
```{r}
plot(iris$Petal.Length, iris$Petal.Width, main="Scatterplot of Iris petal length by width",
   xlab="Petal width ", ylab="Petal length")
```

